Time Series Bootstrapping For Solar Current

### 2021-12-16 deliverables/paper.Rmd
Formatting fix
combine discussion and future

```{r knitr-opts}
knitr::opts_chunk$set(fig.pos = "t", fig.align = 'center', out.width = "75%", out.extra = "")
```

@@

I THINK DISCUSSION AND FUTURE WORK SHOULD BE COMBINED. THEY FLOW INTO EACH OTHER QUITE NICELY. FEEL FREE TO MERGE THEM IF YOU WANT.

# Future Work

>>>>

```{r knitr-opts, echo=FALSE}
knitr::opts_chunk$set(fig.pos = "t", fig.align = 'center', out.width = "75%", out.extra = "")
```

@@
